---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# customsummary

<!-- badges: start -->
<!-- badges: end -->

The customsummary package provides a function, custom_summary(), designed to calculate customized summary statistics (mean, median, and standard deviation) for a numeric vector. It’s flexible in handling missing values and allows for additional arguments to be passed to functions where applicable, such as trim in the mean() function.

## Installation

You can install the development version of customsummary from [GitHub](https://github.com/) with:

``` r
# install.packages("devtools")
devtools::install_github("stat545ubc-2024/customsummary")
```

## Usage

To get started with customsummary, load the library and use custom_summary() on a numeric vector to obtain the mean, median, and standard deviation.

```{r example}
library(customsummary)

# Example 1: Basic usage with a numeric vector
result <- custom_summary(c(1, 2, 3, 4, 5))
print(result)

# Example 2: Handling NA values by setting na.rm = TRUE
result_with_na <- custom_summary(c(1, 2, NA, 4, 5), na.rm = TRUE)
print(result_with_na)

# Example 3: Passing additional arguments (e.g., using trim for mean)
result_with_trim <- custom_summary(c(1, 2, 3, 4, 5), na.rm = TRUE, trim = 0.1)
print(result_with_trim)
```

